\section*{}

\addcontentsline{toc}{section}{References} % adds "References" to table of contents

\begin{thebibliography}{99}

\bibitem{Ali2019}
Ali, A.; Yun, J.; Jalli Ng, H.; Kissinger, D.; Giannini, F.; Colantonio, P. High Performance Asymmetric Coupled Line Balun at Sub-THz Frequency. Appl. Sci. 2019, 9, 1907. https://doi.org/10.3390/app9091907

\bibitem{Li2023}
Y. Li, L. Zhao and W. Yu, "A High-efficiency 135 – 155 GHz Power Amplifier with Compact Three-Conductor Power Combiner Balun in 130-nm SiGe BiCMOS," 2023 IEEE MTT-S International Wireless Symposium (IWS), Qingdao, China, 2023, pp. 1-3, doi: 10.1109/IWS58240.2023.10222761.

\bibitem{Sakai2021}
H. Sakai, K. Takano, S. Hara, A. Kasamatsu and Y. Umeda, "A 220–330 GHz Wideband, Low-Loss and Small Marchand Balun with Ground Shields in SiGe BiCMOS Technology," 2021 IEEE MTT-S International Microwave and RF Conference (IMARC), KANPUR, India, 2021, pp. 1-4, doi: 10.1109/IMaRC49196.2021.9714607.

\begin{comment}
    \bibitem{A 60Ghz wideband active balun using magnitude and phase concurrent correction technique in 65nM CMOS}
S. -C. Chou, F. -C. Huang and C. -K. Wang, "A 60 GHz wideband active balun using magnitude and phase concurrent correction technique in 65nm CMOS," 2012 IEEE Asian Solid State Circuits Conference (A-SSCC), Kobe, Japan, 2012, pp. 273-276, doi: 10.1109/IPEC.2012.6522678.
\end{comment}

\bibitem{Active BALUN with 40 GHz bandwidth at 257 GHz}

J. Hebeler, A. Ç. Ulusoy and T. Zwick, "Active BALUN with 40 GHz bandwidth at 257 GHz in 130 nm SiGe:C," 2022 IEEE 22nd Topical Meeting on Silicon Monolithic Integrated Circuits in RF Systems (SiRF), Las Vegas, NV, USA, 2022, pp. 9-12, doi: 10.1109/SiRF53094.2022.9720063.

\bibitem{Three Compact Active Baluns with High Phase/Amplitude Balance and Low Power in 65-nm CMOS}

B. Deng, M. Liu, H. Guo and L. Sun, "Three Compact Active Baluns with High Phase/Amplitude Balance and Low Power in 65-nm CMOS for Transceiver Applications," 2023 IEEE MTT-S International Wireless Symposium (IWS), Qingdao, China, 2023, pp. 1-3, doi: 10.1109/IWS58240.2023.10222399.

\bibitem{Active Single-Ended to Differential Converter (Balun) for DC up to 70 GHz in 130 nm SiGe}

P. Stärke, V. Rieß, C. Carta and F. Ellinger, "Active Single-Ended to Differential Converter (Balun) for DC up to 70 GHz in 130 nm SiGe," 2019 IEEE BiCMOS and Compound semiconductor Integrated Circuits and Technology Symposium (BCICTS), Nashville, TN, USA, 2019, pp. 1-4, doi: 10.1109/BCICTS45179.2019.8972713

\bibitem{A_compact_capacitor_compensated}

G. S. K. Yong and C. E. Saavedra, "A compact capacitor compensated wideband balun in CMOS technology," 2008 24th Biennial Symposium on Communications, Kingston, ON, Canada, 2008, pp. 306-309, doi: 10.1109/BSC.2008.4563263.

\bibitem{Transformer_matched_gilbert_mixer}

Transformer matched gilbert mixer with active balun for D band transmitter

\bibitem{Ultra Broadband Low-Power 70 GHz Active Balun in 130-nm SiGe BiCMOS}

A. Franzese, M. H. Eissa, T. Mausolf, D. Kissinger, R. Negra and A. Malignaggi, "Ultra Broadband Low-Power 70 GHz Active Balun in 130-nm SiGe BiCMOS," 2020 IEEE BiCMOS and Compound Semiconductor Integrated Circuits and Technology Symposium (BCICTS), Monterey, CA, USA, 2020, pp. 1-4, doi: 10.1109/BCICTS48439.2020.9392960.

\bibitem{SiG13G3}{H. Rücker et al., "SiGe-BiCMOS Technology with 500 GHz fT and 610 GHz fMAX," 2025 IEEE International Electron Devices Meeting (IEDM), San Francisco, CA, USA, 2025, pp. 1-4, doi: 10.1109/IEDM50572.2025.11353861.}

\bibitem{SiG13G2}
130nm BiCMOS Open Source PDK.
URL: \url{https://github.com/IHP-GmbH/IHP-Open-PDK}

\bibitem{Microelectronic circuits}

Sedra, A. S. (2020). Microelectronic circuits / Adel S. Sedra, University of Waterloo, Kenneth C. Smith, University of Toronto, Tony Chan Carusone, University of Toronto, Vincent Gaudet, University of Waterloo. Oxford University Press.

\bibitem{Analysis and Design of Analog Integrated Circuits}
Gray, P. R., Hurst, P. J., Lewis, S. H., \& Meyer, R. G. Analysis and Design of Analog Integrated Circuits. Wiley, 2009. ISBN 9780470245996.

\bibitem{High-Frequency Integrated Circuits}

Voinigescu S. High-Frequency Integrated Circuits. Cambridge University Press; 2013.

\bibitem{Microwave Transistor Amplifiers Analysis and Design}
Gonzalez, G. (1984) Microwave Transistor Amplifiers Analysis and Design. Prentice-Hall, Englewood Cliffs.

\bibitem{Pozar2012}
Pozar, D.M. (2012) Microwave Engineering. 4th Edition, John Wiley \& Sons, Inc., Hoboken.

%cit guadagno di potenza due porte
\bibitem{Revisiting the Power Gains of a Loaded Two-Port}
Ghione, G.; Pirola, M. Revisiting the Power Gains of a Loaded Two-Port: Is There a Missing Element? Electronics 2024, 13, 545. https://doi.org/10.3390/electronics13030545

\bibitem{Keysight Knowledge Center}
Keysight Technologies, Maximum Available Gain (GMAX), Keysight Knowledge Center, 2008, URL: \url{https://docs.keysight.com/display/genesys2009/Maximum%2BAvailable%2BGain}

\bibitem{Microwave differential circuit design using mixed-mode S-parameters}
Eisenstadt, William R.. “Microwave differential circuit design using mixed-mode S-parameters.” (2006).

\bibitem{Considerations and Methods on the Design of sub-THz Amplifiers in SiGe BiCMOS Technology}
 A. Franzese, B. Sutbas, T. Mausolf, M.-D. Wei, R. Negra, and C. Carta, “Considerations and Methods on the Design of Sub-THz Amplifiers in SiGe BiCMOS Technology,” IEEE Microwave and Wireless Technology Letters, 2026

 \bibitem{A 2.4 GHz SiGe HBT high voltage high power amplifier}

Farmer, Thomas \& Darwish, Ali \& Zaghloul, Mona. (2010). A 2.4 GHz SiGe HBT high voltage/high power amplifier. Microwave and Wireless Components Letters, IEEE. 20. 286 - 288. 10.1109/LMWC.2010.2045595.

\bibitem{High power density SiGe millimeter-wave power amplifiers}

Farmer TJ, Darwish A, Huebschman B, Viveiros E, Zaghloul ME. High power density SiGe millimeter-wave power amplifiers. International Journal of Microwave and Wireless Technologies. 2011;3(6):615-620. doi:10.1017/S1759078711000638

\bibitem{ShresthaAmit}

Shrestha, Amit. (2015). A Ka-band power amplifier design for satellite communication in SiGe BiCMOS process. 10.13140/RG.2.1.3803.2083. 

\begin{comment}
\bibitem{Wideband Amplifiers}
Starič, P. \& Margan, E.. (2006). Wideband Amplifiers. 10.1007/978-0-387-28341-8.

\bibitem{A 0.0058-mm2 Inductor-Less CMOS Active Balun With Gain and Phase Errors Within −0.1 ± 0.2 dB and −0.18 ± 1.17° From DC to 8 GHz}
K. Kawahara, Y. Umeda, K. Takano and S. Hara, "A 0.0058-mm2 Inductor-Less CMOS Active Balun With Gain and Phase Errors Within −0.1 ± 0.2 dB and −0.18 ± 1.17° From DC to 8 GHz," in IEEE Transactions on Circuits and Systems I: Regular Papers, vol. 70, no. 6, pp. 2317-2330, June 2023, doi: 10.1109/TCSI.2023.3257089.

\bibitem{Design and Analysis of a 28 GHz Bandwidth DC Coupled Active Balun With Phase-Amplitude Compensation in 40-nm CMOS}
B. Gungor and P. Reynaert, "Design and Analysis of a 28 GHz Bandwidth DC Coupled Active Balun With Phase-Amplitude Compensation in 40-nm CMOS," in IEEE Transactions on Circuits and Systems I: Regular Papers, vol. 72, no. 9, pp. 4420-4430, Sept. 2025, doi: 10.1109/TCSI.2025.3552956.


\bibitem{Design of an original K-band active balun with improved broadband balanced behavior}
\textcolor{red}{** TO CITE?**}C. Viallon, D. Venturin, J. Graffeuil and T. Parra, "Design of an original K-band active balun with improved broadband balanced behavior," in IEEE Microwave and Wireless Components Letters, vol. 15, no. 4, pp. 280-282, April 2005, doi: 10.1109/LMWC.2005.845749.

\bibitem{Dobrowolski2010}{Dobrowolski, Janusz A.. (2010). Microwave Network Design Using the Scattering Matrix. }

\bibitem{On the operation configuration of SiGe HBTs based on power gain analysis}

Zhenqiang Ma and Ningyue Jiang, "On the operation configuration of SiGe HBTs based on power gain analysis," in IEEE Transactions on Electron Devices, vol. 52, no. 2, pp. 248-255, Feb. 2005, doi: 10.1109/TED.2004.842541.

\bibitem{Design considerations for millimeter-wave power HBTs}
S. Tanaka et al., "Design considerations for millimeter-wave power HBTs based on gain performance analysis," in IEEE Transactions on Electron Devices, vol. 45, no. 1, pp. 36-44, Jan. 1998, doi: 10.1109/16.658809.
\end{comment}

\end{thebibliography}